---
title: Pre-med webinar analyses
author: 
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(ggthemes)
library(readxl)
library(waffle)

# source utilities

source(here::here("scripts", "utils_mspa.R"))

# Parameters
input_path <- 
  here::here("data-raw", "webinar.xlsx")

likert_colors <- c("darkgreen","green","orange","red","darkred")

mspa_hex <- "#666699"


agreement_levels <- 
  c(
    "Strongly disagree", 
    "Somewhat disagree", 
    "Neither agree nor disagree", 
    "Somewhat agree", 
    "Strongly agree"
  )

concern_levels <- 
  c(
    "Strongly concerned", 
    "Somewhat concerned", 
    "Moderately concerned", 
    "Slightly concerned", 
    "Not at all concerned"
  ) %>% 
  rev()

prepared_levels <- 
  c(
    "Strongly prepared",
    "Moderately prepared", 
    "Somewhat prepared", 
    "Slightly prepared", 
    "Not at all prepared"
  ) %>% 
  rev()

asset_levels <- 
  c(
    "Hindrance", 
    "Slight hindrance", 
    "Neither hindrance/asset", 
    "Slight asset", 
    "Asset"
  )

agreement_variables <- 
  c(
    "pre_confident_out", 
    "pre_support_advisors", 
    "pre_important_community", 
    "pre_value_mentors_advisors", 
    "post_confident_out", 
    "post_support_advisors", 
    "post_important_community", 
    "post_value_mentors_advisors", 
    "webinar_helped"
  )

col_names <-
  c(
    "pre_confident_out", 
    "pre_support_advisors", 
    "pre_important_community", 
    "pre_value_mentors_advisors", 
    "pre_concern_applying", 
    "pre_prepared_applying", 
    "pre_asset_hindrance", 
    "pre_asset_hindrance_comment", 
    "what_are_your_concerns",
    "experiences_premed_advising",
    "post_confident_out", 
    "post_support_advisors", 
    "post_important_community", 
    "post_value_mentors_advisors", 
    "webinar_helped", 
    "post_concern_applying", 
    "post_prepared_applying", 
    "post_asset_hindrance", 
    "asset_hindrance_changed", 
    "new_concerns", 
    "final_comments"
  )
  
#===============================================================================

```

## Read in and clean data

```{r, read_data}
webinar_data <- 
  input_path %>% 
  read_excel(col_names = col_names, skip = 2) %>% 
  mutate(
    respondent_id = 1:n(), 
    across(contains("asset"), ordered, levels = asset_levels), 
    across(any_of(agreement_variables), ordered, levels = agreement_levels), 
    across(contains("prepared"), ordered, levels = prepared_levels), 
    across(contains("concern"), ordered, levels = concern_levels)
  )
  
col_descriptors <- 
  input_path %>% 
  read_excel() %>% 
  .[1,] %>% 
  as.character() %>% 
  setNames(object = ., nm = col_names)

```

```{r, eval = FALSE}
colnames(webinar_data)
```


A function for plotting and significance testing for pre- and post-webinar questions
```{r}
analyze_pre_post <- function(name = "") { 
  
  subtitle <- 
    col_descriptors[str_c("pre_",name)] %>% 
    str_remove(pattern = "^.+-") %>% 
    str_wrap(width = 70)
  
 my_data <- 
   webinar_data %>% 
    select(contains(name), respondent_id, -contains("comment"), -contains("changed")) %>% 
    pivot_longer(
      cols = contains(name), 
      names_to = c("timepoint"), 
      values_to = "response"
    ) %>% 
    drop_na() %>%
   group_by(respondent_id) %>% 
   filter(n() > 1) %>% 
   ungroup() %>% 
    mutate(
      timepoint = 
        str_extract(timepoint, pattern = "^[:alpha:]+") %>% 
        factor(levels = c("pre", "post"))
    )
 
 contingency_table <-
   table(
     my_data %>% 
       pull(timepoint), 
     my_data %>% 
       pull(response)
   ) %>% 
   t()
 
 overall_chi_squared <- 
   contingency_table %>% 
   chisq.test(simulate.p.value = TRUE, B = 2000)
 
 t_statistic <- t.test(
   x = 
     my_data %>% 
     filter(timepoint == "pre") %>% 
     pull(response) %>% 
     as.numeric(), 
   y =
     my_data %>% 
     filter(timepoint == "post") %>% 
     pull(response) %>% 
     as.numeric(),
   paired = TRUE
 )
 
 mean_data <- 
   my_data %>% 
   group_by(timepoint) %>% 
   summarize(response = mean(as.numeric(response)))
    
 
 my_likert <- 
   my_data %>% 
   likert_plot(
     my_var = response, 
     break_var = timepoint, 
     title = NULL, 
     n = n_distinct(my_data$respondent_id)
   ) + 
   labs(
     caption = 
       str_glue(
         "N = {my_n}; p = {my_p}", 
         my_n = n_distinct(my_data$respondent_id), 
         my_p = t_statistic$p.value %>% round(4)
       )
   )
  
  my_plot <-
    my_data %>% 
    ggplot(aes(x = timepoint, y = response)) + 
    geom_line(aes(group = respondent_id), color = "gray", alpha = 0.6) + 
    geom_count(color = "gray", alpha = 0.6) +  
    geom_line(
      aes(x = timepoint, y = response, group = 1), 
      data = mean_data, 
      color = "black", 
      size = 1.5
    ) + 
    geom_point(
      aes(x = timepoint, y = response), 
      data = mean_data, 
      color = "black", 
      size = 4
    ) + 
    scale_x_discrete(drop = FALSE) + 
    scale_size_area(breaks = 1:5) + 
    labs(
      subtitle = subtitle, 
      x = NULL, 
      y = NULL, 
      size = "Number of students",
      caption = 
        str_glue(
          "N = {my_n}; p = {my_p}", 
          my_n = n_distinct(my_data$respondent_id), 
          my_p = t_statistic$p.value %>% round(4)
        )
    )
  
  my_result <- 
    list(
      means = mean_data, 
      plot = my_plot, 
      likert = my_likert, 
      t = t_statistic
    )
  
  return(my_result)
}
```

## Visualizations

### Did the webinar help?

```{r}
n <- 
  webinar_data %>% 
  filter(!is.na(webinar_helped)) %>% 
  count() %>%
  pull(n)

 ns <- 
  webinar_data %>% 
  filter(!is.na(webinar_helped)) %>% 
  count(webinar_helped) %>% 
   pull(n)
 
 n_somewhat <- ns[[1]]
 n_strongly <- ns[[2]]

webinar_data %>% 
  drop_na(webinar_helped) %>% 
  count(webinar_helped) %>% 
  ggplot(aes(fill = webinar_helped, values = n)) + 
  geom_waffle(color = "white", n_rows = 3, size = 0.25, make_proportional = FALSE) + 
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_continuous(
    labels = function(x) x * 3, 
    expand = c(0, 0)
  ) +
  ggthemes::scale_fill_tableau(
    name = NULL, 
    labels = 
      c(
        str_glue("Somewhat agree ({n_somewhat})"), 
        str_glue("Strongly agree ({n_strongly})")
      ),
    palette = "Tableau 10"
  ) +
  coord_equal() +
  theme_minimal() + 
  theme(
    strip.text = element_text(angle = 0, hjust = 0), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(), 
    legend.position = "bottom"
  ) + 
  labs(
    subtitle = "\"This webinar helped me decide how to best to apply as an LGBTQ+ student\"",
    x = "Number of students"
  )
```

So overall, it looks like most students self-reported that the webinar was helpful to them.

### Pre and post comparisons

Now we can delve into some of the pre- and post-webinar comparisons. For these analyses, I mostly 
treated the likert data on an ordinal 1-5 scale. For the significance testing, I either averaged the 
ordinal values for pre- and post- and performed a paired t-test or used a Chi-squared test for goodness 
of fit on the overall contingency tables. I also made two ways of visualizing the responses...any of this 
can be changed, but it was my first-pass for feedback. 

Note that for the line plots, the big bold line represents the mean change and each of the gray, smaller 
lines represents an individual person.

Also note that, right now, for any given question, I throw away all the responses that don't have both 
pre- and post-webinar answers. For many people, there are answers in the pre-webinar section (but not the
post-webinar section), and in theory I could include those responses in the analyses if we want...I'm trying
to make up my mind if that's something I want to do, since it will change the statistics a little bit. 


**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "confident_out")
```


**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "support_advisors")
```

**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "important_community")
```

**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "value_mentors_advisors")
```

**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "concern_applying")
```


**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "prepared_applying")
```

**Confidence applying to medical school as an out LGBTQ+ person**
```{r}
analyze_pre_post(name = "asset_hindrance")
```




## Final comments

```{r}
webinar_data %>% 
  select(`Any final comments?` = final_comments) %>% 
  drop_na() %>% 
  knitr::kable()
```

